Untitled

### 2024-01-28 Evalsims.Rmd
sims

```{r}
library(data.table)
library(ggplot2)
out <- rbindlist(lapply(c(1, 1.5, 2, 2.5, 3), function(shape) {
  data <- fread(paste0("results/sims_calibration_1000_rf_3_0.1_", shape, "_0.6.csv"))
  data$shape <- shape
  data
}))

out <- out[out$method %in% c("cal_binning_5", "mondrian_5", "marginal", "isotonic", "conditional")]
ggplot(out[out$shape == 1], aes(x = bin, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3) + theme_bw()

ggplot(out[out$shape == 1], aes(x = bin, y = width, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw()

ggplot(out[out$bin == "marginal"], aes(x = shape, y = width, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw()

@@

```{r}
library(data.table)
library(ggplot2)
library(latex2exp)
method_names <- c("HistCAL (5 bins)", "Conditional (Gibbs)", "IsoCAL (ours)", "Unconditional", "Mondrian (5 bins)", "Oracle")
names(method_names) <- c("cal_binning_5", "conditional", "isotonic","marginal", "mondrian_5", "oracle")

out <- fread(paste0("results/sims_coverage_1000_gam_5_0.1_1_0.6.csv"))

out <- out[out$method %in% c("oracle", "mondrian_5", "marginal", "isotonic", "conditional")]
out$method <- method_names[match(out$method, names(method_names))]

out$method <- factor(out$method, levels = 
                     c("IsoCAL (ours)", "Conditional (Gibbs)" , "Unconditional", "HistCAL (5 bins)", "Mondrian (5 bins)", "Oracle")  )

@@

library(patchwork)
combined_plot <- plot1 + plot2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
combined_plot
# this plot is good
```

>>>>

```{r}
library(data.table)
library(ggplot2)
out <- rbindlist(lapply(c(1, 1.5, 2, 2.5, 3), function(shape) {
  data <- fread(paste0("results/sims_calibration_1000_rf_5_0.1_", shape, "_0.6.csv"))
  data$shape <- shape
  data
}))

method_names <- c("HistCAL-CP (5 bins)", "Conditional-CP", "SC-CP (ours)", "Unconditional-CP", "Mondrian-CP (5 bins)", "Oracle")
names(method_names) <- c("cal_binning_1", "conditional", "isotonic","marginal", "mondrian_1", "oracle")

out <- out[out$method %in% c("cal_binning_1", "mondrian_1", "marginal", "isotonic", "conditional", "oracle")]

out$method <- method_names[match(out$method, names(method_names))]

out$method <- factor(out$method, levels = 
                     c("SC-CP (ours)", "Conditional-CP" , "Unconditional-CP", "HistCAL-CP (5 bins)", "Mondrian-CP (5 bins)", "Oracle")  )

plt1 <- ggplot(out[out$bin == "marginal"], aes(x = shape, y = width, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(x = TeX("Distribution shift in training data ($\\kappa_{train}$)"), y = "Interval Width") +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank())) + 
 theme(legend.text = element_text(size = 11), legend.key.size = unit(2, "lines"))

plt1
ggsave("plots/calibration_shift.pdf" , width = 7, height = 5)

plt2 <- ggplot(out[out$bin == "marginal"], aes(x = shape, y = coverage, color = method)) + geom_point(aes(shape = method), size = 3)   + theme_bw() + labs(x = TeX("Distribution shift in training data ($\\kappa_{train}$)"), y = TeX("Coverage ($\\alpha = 0.1$)")) +   guides(color = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank())) + 
 theme(legend.text = element_text(size = 11), legend.key.size = unit(2, "lines"))

plt2

#combined_plot <- plt1 + plt2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")

#ggsave("plots/calibration_shift.pdf" , width = 7, height = 5)

@@

```{r}
library(data.table)
library(ggplot2)
library(latex2exp)
method_names <- c("HistCAL (5 bins)", "Conditional-CP", "SC-CP (ours)", "Unconditional-CP", "Mondrian-CP (5 bins)", "Oracle")
names(method_names) <- c("cal_binning_5", "conditional", "isotonic","marginal", "mondrian_5", "oracle")

out <- fread(paste0("results/sims_coverage_1000_gam_5_0.1_1_0.6.csv"))
#out <- fread(paste0("results/sims_calibration_1000_rf_5_0.1_1_0.6.csv"))

out <- out[out$method %in% c("oracle", "cal_binning_5", "mondrian_5", "marginal", "isotonic", "conditional")]
out$method <- method_names[match(out$method, names(method_names))]

out$method <- factor(out$method, levels = 
                     c("SC-CP (ours)", "Conditional-CP" , "Unconditional-CP", "HistCAL (5 bins)", "Mondrian-CP (5 bins)", "Oracle")  )

@@

library(patchwork)
combined_plot <- plot1 + plot2 + plot_layout(guides = "collect") & theme(legend.position = "")
combined_plot
print(combined_plot)

ggsave("plots/conditional_coverage.pdf", plot = combined_plot, width = 6, height = 3.5)
# this plot is good

plot1 + plot2 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

### 2024-01-28 plot_curves.Rmd
sims

```{r}
library(data.table)
library(ggplot2)
library(latex2exp)
data <- rbindlist(lapply(c( 50, 100, 300, 1000), function(n) {
  data <- read.csv(paste0("plots/curves_", n, "_0.5.csv"))
  data$n <- n
  return(data)
}))
data[data$method == "Isotonic", "method"] <- "Isotonic (ours)"
data[data$method == "isotonic", "method"] <- "Isotonic (ours)"
data[data$method == "conditional", "method"] <- "Conditional (Gibbs)"
data[data$method == "Conditional (kernel)", "method"] <- "Conditional (Gibbs)"
data[data$method == "marginal", "method"] <- "Marginal"

@@

#X_grid <- seq(0, 1, length = 10000)

# new_data <- rbindlist(unlist(lapply(unique(data$method), function(method) {
#   lapply(unique(data$n), function(n) {
#     data_sub <- data[data$method == method & data$n == n,]
#     if(method == "isotonic") { 
#       x_sort <- data_sub$X[order(data_sub$X)]
#       lower_sort <- data_sub$lower[order(data_sub$X)][!duplicated(x_sort)]
#       upper_sort <- data_sub$upper[order(data_sub$X)][!duplicated(x_sort)]
#       x_sort <- x_sort[!duplicated(x_sort)]
#       
#       fit_lower <- stepfun(x_sort, c(lower_sort, lower_sort[length(lower_sort)]))
#       fit_upper <- stepfun(x_sort, c(upper_sort, upper_sort[length(upper_sort)]))
#     } else {
#       fit_lower <- ksmooth(x = data_sub$X, y = data_sub$lower, range.x = c(0,1), n.points = 1000, kernel = "normal")
#       fit_upper <- ksmooth(x = data_sub$X, y = data_sub$upper, range.x = c(0,1), n.points = 1000, kernel = "normal")
#       
#       new_data <- data.table(method = method, n = n, X = fit_lower$x, 
#                              lower = fit_lower$y,
#                              upper = fit_upper$y
#       )
#     }
#     
#     
#     return(new_data)
#   })}), recursive = FALSE))
# 
# 
linetypes <- c("solid", "dotted", "dashed")
data$method <- factor(data$method, levels = c("Isotonic (ours)", "Conditional (Gibbs)", "Marginal"))

@@

plt <- ggplot(data, aes(x = X, color = method, linetype = method)) +
  geom_step(aes(y = lower), size = 0.8)  +
  geom_step(aes(y = upper), size = 0.8) +
  geom_line(data = preds_oracle, aes(x = X, y = lower), color = "black", alpha = 1, linetype = "solid")  +
  geom_line(data = preds_oracle, aes(x = X, y = upper), color = "black", alpha = 1, linetype = "solid") +
  theme(legend.position="bottom") + theme_bw() + labs(color = "", y = "Y") + facet_wrap(~ n, labeller = as_labeller(appender, 
                            default = label_parsed) ) +  labs(color  = "", linetype = "", shape = "")   + theme(legend.key.size = unit(1, "cm"), legend.position = "bottom", legend.direction = "horizontal",
                                                                                                    legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-10,-10,-10,-10))  +
  scale_linetype_manual(values=c("solid", "dotted", "dashed", "dotdash"))

@@

ggsave(file="plots/curves_pooled.pdf", width=7, height=5)
# 
# plt <- ggplot(data, aes(x = X, color = method, linetype = method)) +
#   geom_step(aes(y = lower), size = 0.8)  +
#   geom_step(aes(y = upper), size = 0.8) +
#   theme(legend.key.size = unit(1, "cm"), legend.direction = "horizontal")  +
#   scale_linetype_manual(values=c("solid", "dotted", "dashed", "dotdash")) +
#   labs(color  = "", linetype = "", shape = "")  
# 
# library(cowplot)
# library(grid)
# legend <-  get_legend(plt)
# pdf("plots/curves_pooled_legend.pdf", width = 5, height = 1) # Adjust the width and height as needed
# grid.draw(legend)
# dev.off()
# 
#

ggsave(file="plots/curves_pooled_legend.pdf", width=7, height=5)

>>>>

```{r}
library(data.table)
library(ggplot2)
library(latex2exp)
data <- rbindlist(lapply(c( 50, 100, 300, 1000), function(n) {
  data <- read.csv(paste0("plots/curves_", n, "_0.5.csv"))
  data$n <- n
  return(data)
}))
data[data$method == "Isotonic", "method"] <- "SC-CP (ours)"
#data[data$method == "isotonic", "method"] <- "Isotonic (ours)"
#data[data$method == "conditional", "method"] <- "Conditional (Gibbs)"
data[data$method == "Conditional (kernel)", "method"] <- "Conditional-CP"
data[data$method == "Marginal", "method"] <- "Unconditional"

@@

data$method <- factor(data$method, levels = c("SC-CP (ours)", "Conditional-CP", "Unconditional"))

@@

plt <- ggplot(data, aes(x = X, color = method, linetype = method)) +
  geom_step(aes(y = lower), size = 0.8)  +
  geom_step(aes(y = upper), size = 0.8) +
  geom_line(data = preds_oracle, aes(x = X, y = lower), color = "black", alpha = 1, linetype = "solid")  +
  geom_line(data = preds_oracle, aes(x = X, y = upper), color = "black", alpha = 1, linetype = "solid") +
  theme(legend.position="bottom") + theme_bw() + labs(x = "Covariate (X)", color = "", y = "Outcome (Y)") + facet_wrap(~ n, labeller = as_labeller(appender, 
                            default = label_parsed) ) +  labs(color  = "", linetype = "", shape = "")   + theme(legend.key.size = unit(1, "cm"), 
        legend.text = element_text(size = 12),  # Adjust text size here
        legend.title = element_text(size = 14), # Adjust title size here
        legend.position = "bottom", 
        legend.direction = "horizontal",
        legend.margin = margin(0,0,0,0),
        legend.box.margin = margin(-10,-10,-10,-10)) +
  scale_linetype_manual(values = c("solid", "dotted", "dashed", "dotdash"))

#theme(legend.key.size = unit(1, "cm"), legend.position = "bottom", legend.direction = "horizontal",
                                                                                            #  legend.margin=margin(0,0,0,0),
    #    legend.box.margin=margin(-10,-10,-10,-10))  +
  #scale_linetype_manual(values=c("solid", "dotted", "dashed", "dotdash"))

@@

ggsave(file="plots/curves_pooled.pdf", width=7, height=5)
# 
# plt <- ggplot(data, aes(x = X, color = method, linetype = method)) +
#   geom_step(aes(y = lower), size = 0.8)  +
#   geom_step(aes(y = upper), size = 0.8) +
#   theme(legend.key.size = unit(1, "cm"), legend.direction = "horizontal")  +
#   scale_linetype_manual(values=c("solid", "dotted", "dashed", "dotdash")) +
#   labs(color  = "", linetype = "", shape = "")  
# 
# library(cowplot)
# library(grid)
# legend <-  get_legend(plt)
# pdf("plots/curves_pooled_legend.pdf", width = 5, height = 1) # Adjust the width and height as needed
# grid.draw(legend)
# dev.off()
# 
#  
#X_grid <- seq(0, 1, length = 10000)

# new_data <- rbindlist(unlist(lapply(unique(data$method), function(method) {
#   lapply(unique(data$n), function(n) {
#     data_sub <- data[data$method == method & data$n == n,]
#     if(method == "isotonic") { 
#       x_sort <- data_sub$X[order(data_sub$X)]
#       lower_sort <- data_sub$lower[order(data_sub$X)][!duplicated(x_sort)]
#       upper_sort <- data_sub$upper[order(data_sub$X)][!duplicated(x_sort)]
#       x_sort <- x_sort[!duplicated(x_sort)]
#       
#       fit_lower <- stepfun(x_sort, c(lower_sort, lower_sort[length(lower_sort)]))
#       fit_upper <- stepfun(x_sort, c(upper_sort, upper_sort[length(upper_sort)]))
#     } else {
#       fit_lower <- ksmooth(x = data_sub$X, y = data_sub$lower, range.x = c(0,1), n.points = 1000, kernel = "normal")
#       fit_upper <- ksmooth(x = data_sub$X, y = data_sub$upper, range.x = c(0,1), n.points = 1000, kernel = "normal")
#       
#       new_data <- data.table(method = method, n = n, X = fit_lower$x, 
#                              lower = fit_lower$y,
#                              upper = fit_upper$y
#       )
#     }
#     
#     
#     return(new_data)
#   })}), recursive = FALSE))
# 
#

#ggsave(file="plots/curves_pooled_legend.pdf", width=7, height=5)
